Wrestling according to the rules of United World Wrestling
requires the presence of three officials at every match
-- a~mat referee who communicates decisions through hand
gestures, a~judge who manually records these decisions on
a~paper scoring card, and a~mat chairman who supervises
their cooperation. This method of recording slows down
the match. This thesis explores whether the process can
be simplified using commercially available smartwatches,
without the need for machine learning techniques, thereby
reducing the number of officials required to conduct
a~match. The proposed solution uses an Amazfit T-Rex~3
smartwatch running the Zepp~OS operating system, worn on
the referee's left wrist, which captures motion through
its accelerometer and gyroscope. The data is evaluated 
by a~companion Android application using
a~threshold-based algorithm calibrated for eight referee
gestures defined by the rules of United World Wrestling.
The gestures were designed to follow the referee's
natural mat gesticulation, so that no artificial movements
need to be learned that could cause confusion. The
reliability of the system was evaluated across three
testing phases comprising 420 recognition attempts,
achieving an accuracy of 99.4\,\% for isolated gestures
under ideal conditions, 96.2\,\% for the complete
wrestling scenario, and between 83.1\,\% and 90.8\,\% for
two external testers. The main limitation is the
dependence of the threshold-based algorithm on the
individual style of gesture execution, which could be
addressed in the future by introducing a~calibration
phase tailored to each referee.